Supplementary Information

### 2021-01-05 doc/manuscript/MEE_manuscript.Rmd
knit in latest results (results not yet updated)
#105

![**Figure 6 | DRAFT FIGURE. GLS model with and without year, maybe decadal analysis plot. IT WOULD BE BEST TO COMBINE THE 2 DBH FIGURES (PANELS 1,2). CURRENT EXAMPLE IS JUST SCOTTY CREEK, BUT IT WOULD BE GOOD TO SHOW AT LEAST ONE OTHER.](tables_figures/year_figure_sketch.png)

>>>>

![**Figure 6 | (Responses to year, for species tested).](tables_figures/Year_responses.png)
